---
title: "ML_PeanutOil"
output: html_document
date: "2024-03-08"
---

import data
```{r}
library(httr)
url <- "https://github.com/tradanghi1999/RStudy/raw/main/regression/multi%20linear%20regression/Data%20MR.xlsx"
raw_xlsx <- GET(url)$content
tmp <- tempfile(fileext = '.xlsx')
writeBin(raw_xlsx, tmp)
peanutOil <- readxl::read_excel(tmp, sheet = 1, range = "A1:F17")
```
#a. Fit a multiple linear regression model relating yield to these regressors.
```{r}



model <- lm(peanutOil$Yield~., data=peanutOil)
dSummary <- summary(model)
print(dSummary)
print(names(dSummary))

```
#b. Test for significance of regression. What conclusions can you draw?
```{r}
lmp <- function (tdSummary) {
	f <- tdSummary$fstatistic
	p <- pf(f[1],f[2],f[3],lower.tail=F)
	attributes(p) <- NULL
	return(p)
}


p_value = lmp(dSummary)
if(p_value <.05) {
  print(paste0("p_value is: ", p_value, " < 0.05, regression is considered to be significant"))
} else {
  print(paste0("p_value is: ", p_value, " > 0.05, regression is considered not to be significant"))
}
```

#• c. Use t tests to assess the contribution of each regressor to the model. Discuss your finding

```{r}
print(coef(dSummary)[, "Pr(>|t|)"])

```
For only Pr(>|t|) of  Temperature (oC) and Particle Size (mm) are below < 0.05.
We consider these two variable being significant and others are not.


#d. Calculate R2 and RAdj2 for this model. Compare these values to the R 2 and RAdj2 for the multiple linear regression model relating yield to temperature and particle size. Discuss your results

```{r}
#print r-squared
print(dSummary$r.squared)

#print adj-r-squared
print(dSummary$adj.r.squared)


#the multiple linear regression model relating yield to temperature and particle size
anodModel <- lm(peanutOil$Yield~`Temperature (oC)` + `Particle Size (mm)`, data = peanutOil)

dAnodSummary <- summary(anodModel)



#print r-squared
print(dAnodSummary$r.squared)

#print adj-r-squared
print(dAnodSummary$adj.r.squared)


```
the first model appears to be more correct than the second one (considering r-squared) but the second one is more precise when considering in regard to the contribution of the variables. (adj-r-squared)