---
title: "ML_WineQuality"
output: html_document
date: "2024-03-08"
---

import data
```{r}
library(httr)
url <- "https://github.com/tradanghi1999/RStudy/raw/main/regression/multi%20linear%20regression/Data%20MR.xlsx"
raw_xlsx <- GET(url)$content
tmp <- tempfile(fileext = '.xlsx')
writeBin(raw_xlsx, tmp)
wineQuality <- readxl::read_excel(tmp, sheet = 5, range = "A1:G39")
```


#• a. Fit a multiple linear regression model relating wine quality to these regressors.

```{r}
wineQuality_noReg <- subset(wineQuality, select = -Region)
model <- lm(wineQuality_noReg$Quality~., data = wineQuality_noReg)
```



# b. Test for significance of regression. What conclusions can you draw?
```{r}
print(summary(model))
```
p-value: 4.703e-08, the regression is considered to be significant.


# c. Use t tests to assess the contribution of each regressor to the model. Discuss your findings.

As the t-test points out, only Flavor and Oakiness seem to have significant contribution to the model for their Pr(>|t|) < alpha

# d. Calculate R 2 and RAdj2 for this model. Compare these values to the R 2 and RAdj2 for the linear regression model relating wine quality to aroma and flavor. Discuss your results.


Multiple R-squared:  0.7206,	Adjusted R-squared:  0.6769 

Other model:

```{r}
odModel <- lm(wineQuality_noReg$Quality~Flavor + Aroma, data = wineQuality_noReg)
summary(odModel)

```
The odModel sseem to have better significance, but the Adjusted R-squared:  0.639 is lower which points out that it can have more error when predicting.

# e. Find a 95 % CI for the regression coefficient for flavor for both models in part d. Discuss any differences.

```{r}
print(confint(model, level=0.95))
print(confint(odModel, level=0.95))
```
Flavor (model)      0.54811681  1.7885307
Flavor (odModel)      0.58032952 1.760003

The CI of later Flavor is narrower, which mean in this model, Flavor is considered to be less variant. As for the later is less precise, this Flavor seems to fit with the overall idea.


# f. Fit a regression model using clarity, aroma, body, flavor, and oakiness as the regressors. Investigate this model for influential observations and comment on your findings

We will use cook distace to investigate this problem

```{r}

cooksD <- cooks.distance(model)
influential <- cooksD[(cooksD > (3 * mean(cooksD, na.rm = TRUE)))]
influential
names_of_influential <- names(influential)
outliers <- wineQuality_noReg[names_of_influential,]
wineQuality_noReg_without_outliers <- wineQuality_noReg %>% anti_join(outliers)

#print and plot
print(outliers)

# Assume df_normal and df_outliers are your dataframes
# and 'x' and 'y' are the columns you want to plot

library(ggplot2)

###############################################
#Clarity Plot
# Create a ggplot object with the normal points
p <- ggplot(wineQuality_noReg_without_outliers, aes(x = Clarity, y =Quality)) +
  geom_point(color = "black")

# Add the outliers in red
p <- p + geom_point(data = outliers, aes(x = Clarity, y= Quality), color = "red")

# Print the plot
print(p)
###############################################

#Flavor Plot
p <- ggplot(wineQuality_noReg_without_outliers, aes(x = Flavor        , y =Quality)) +
  geom_point(color = "black")

# Add the outliers in red
p <- p + geom_point(data = outliers, aes(x = Flavor, y= Quality), color = "red")

# Print the plot
print(p)

################################################

p <- ggplot(wineQuality_noReg_without_outliers, aes(x = Oakiness             , y =Quality)) +
  geom_point(color = "black")

# Add the outliers in red
p <- p + geom_point(data = outliers, aes(x = Oakiness     , y= Quality), color = "red")

# Print the plot
print(p)

###################################

model2 <- lm(wineQuality_noReg_without_outliers$Quality~., data = wineQuality_noReg_without_outliers)
summary(model2)




```



In these plot we can see that these outliers is some how not lie together with other pointes, which usually in the edge of the plot

As describing one point is so normal except its Clarity is so low, and the other is normal except its Quality is so low