---
title: "Ex1"
output: html_notebook
---


Import data into a vavariable:
```{r}
library(httr)
url <- "https://raw.githubusercontent.com/tradanghi1999/RStudy/main/regression/multi%20linear%20regression/ex1data1.txt"
response <- GET(url)
raw_text <- content(response, "parsed")
ex1data1 <- read.table(text = raw_text, sep=",", header = TRUE)

```

Explore data:
```{r}
library(ggplot2)
print(dim(ex1data1))
print(ggplot(data=ex1data1,aes(x=Pop,y=FoodtruckProfit)) + geom_point(col="blue"))
```

After exploring the data, predict that there is a linear relationship between x and y:

```{r}
#model
model <- lm(ex1data1$FoodtruckProfit~Pop, data = ex1data1)
#visualize model
print(ggplot(data = ex1data1, aes(x = Pop, y = FoodtruckProfit)) + geom_point() + geom_smooth(method='lm', se=TRUE))
```

Summary and commment:
```{r}
#summary the model
print(summary(model))
```
1) Pr(>|t|) = 2x10^(-16) < 0.05. 
   Conclude: There is indeed a linear dependence of y = FoodtruckProfit on x = Pop

2) Multiple R-squared:  0.702
   The variance of real data and the model could be up to 70.2%. 
   Which means when the model explains 70.2% for the change in FoodtruckProfit by using the regressor (Pop)
    
3) Post-inspection of the model with F-statistic:
    p-value: = 2.2 * 10 (-16) < 0.05 
    Conclue: the model is accepted
    
    

Post-check the model, Residual
```{r}
plot(model)
```
