---
title: "Ex2"
output: html_notebook
---


Import data into a vavariable:
```{r}
library(httr)
url <- "https://raw.githubusercontent.com/tradanghi1999/RStudy/main/regression/multi%20linear%20regression/ex1data2.txt"
response <- GET(url)
raw_text <- content(response, "parsed")
ex1data2 <- read.table(text = raw_text, sep=",", header = TRUE)

```

Explore data:
```{r}
library(ggplot2)
print(dim(ex1data2))
pairs(ex1data2[,c(1,2,3)])
```

After exploring the data, predict that there is a linear relationship between x = Size and y = Price:

```{r}
#model
model <- lm(ex1data2$Price~Size, data = ex1data2)
#visualize model
print(ggplot(data = ex1data2, aes(x = Size, y = Price)) + geom_point() + geom_smooth(method='lm', se=TRUE))
```

Summary and commment:
```{r}
#summary the model
print(summary(model))
```
1) Pr(>|t|) = 2x10^(-14) < 0.05. 
   Conclude: There is indeed a linear dependence of y = Price on x = Size

2) Multiple R-squared:  0.731
   Which means if the model can use the regressors mentioned to predict 73.1% the value of the response.
    
3) Post-inspection of the model with F-statistic:
    p-value: = 2.2 * 10 (-14) < 0.05 
    Conclue: the model is accepted
    

At the end, we examine another model to be sure:
```{r}
model2 <- lm(ex1data2$Price~., data = ex1data2)
print(summary(model2))

```
Comment:
  Adjusted R-squared:  0.7208 < 0.725 
  Therefore, model1 is better than model2 is angles of number of variables and correction