---
title: "ex3"
output: html_document
date: "2024-03-05"
---

Import data into a vavariable:
```{r}
library(httr)
url <- "https://raw.githubusercontent.com/tradanghi1999/RStudy/main/regression/multi%20linear%20regression/ex3.txt"
response <- GET(url)
raw_text <- content(response, "parsed")
ex3data <- read.table(text = raw_text, sep="\t", header = TRUE)

```

Explore data:
```{r}
library(ggplot2)
print(dim(ex3data))
pairs(ex3data[, 2:8])
```
Prediction and Model

```{r}
library(FactoMineR)
#we try
#res = RegBest(y=ex3data$O.liking, x = ex3data[, 2:7], method= c("adjr2"), nbest=1)
#res$best
```
For there is the error in the leaps, which mean the function detects a linear dependency between variables.

```{r}
library(FactoMineR)
#we try again
res = RegBest(y=ex3data$O.liking, x = ex3data[, 2:6], method= c("adjr2"), nbest=1)
res$best
```
For  p-value: 0.2123 we conclude the model is not valid.
And we also try to test the model of bodytaste

```{r}
library(FactoMineR)
#we try again
res = RegBest(y=ex3data$bodytaste, x = ex3data[, 2:6], method= c("adjr2"), nbest=1)
res$best
```
We conclude thre is a linear dependency between bodytaste and another T.* variable

We will try another model

```{r}
res = lm(ex3data$O.liking~bodytaste, data=ex3data)
print(summary(res))

```
