---
title: "pca_salmon"
output: html_document
date: "2024-03-23"
---


Import data into a vavariable:
```{r}

salmon.data <- read.delim2("~/MVA2024/Salmon_characteristics.txt")

summary(salmon.data)

```

[Instructor] The MEAN value is usually near 0, which mean these data has been proccessed before


```{r}
pairs(salmon.data[,2: 8])

# Load required packages
library(corrplot)

# Create a correlation matrix from your data frame
cor_matrix <- cor(salmon.data[,2:17])

# Plot the correlation matrix using corrplot
corrplot(cor_matrix, method = "color", type = "upper", order = "hclust")
```
```{r}
# Load required packages (if not already loaded)
library(ggplot2)

# Plot a histogram of values in the "column_name" column
ggplot(data = salmon.data, aes(x = salt)) +
  geom_histogram(binwidth = 1, fill = "blue", color = "black") +
  labs(x = "Column Name", y = "Frequency", title = "Histogram of Salt")
```

```{r}



library(FactoMineR)
library(factoextra)
library(ggplot2)
library(corrplot)




```






```{r}



library(FactoMineR)
library(factoextra)
library(ggplot2)
library(corrplot)
#pca model
res.PCA <-  PCA(salmon.data, scale.unit = TRUE,quali.sup=c(1,18),graph = T)

#print the eigenvalue
print(get_eigenvalue(res.PCA))

#check The quality of representation
var <- get_pca_var(res.PCA)
print(corrplot(var$cos2, is.corr=FALSE))


# Color by cos2 values: quality on the factor map
fviz_pca_var(res.PCA, col.var = "cos2",
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"), 
             repel = TRUE # Avoid text overlapping
             )
#check contribution of variance to PC
# Contributions of variables to PC1
fviz_contrib(res.PCA, choice = "var", axes = 1, top = 12)
# Contributions of variables to PC2
fviz_contrib(res.PCA, choice = "var", axes = 2, top = 12)
# Contributions of variables to PC3
fviz_contrib(res.PCA, choice = "var", axes = 3, top = 12)

```

As we can see from the eigenvalue table, that 
Dim.1  5.46821199      34.17632493                    34.17632
Dim.2  2.51222592      15.70141202                    49.87774
Dim.3  1.80173714      11.26085714                    61.13859
Dim.4  1.33622262       8.35139136                    69.48999
Dim.5  1.24367295       7.77295594                    77.26294

These DIM.s has eigenvalue > 1, but only three of them has  variance.percent > 10% Therefore we consider that Dim1 -> Dim3 is considered the PCA.

With #check The quality of representation, we can see that in these projection
our variables (Dim1 -> Dim3) is consider to be well-presented (only phenol and PH is not).

Using #check contribution of variance to PC
We have some conclusion that:
Lactic.flora  -> salt is considered to contribute most to the variance of Dim1
L -> b is considered to contribute most to the variance of Dim2
water, lipid is considered to contribute most to the variance of Dim3

[Instruction] 
Tieu chi 1: eigenvalue            ======> 5 truc
Tieu chi 2: variance.percent      ======> 3 truc
Tieu chi chay stimulation: 17, 30 -> 31.2 ======> 2 truc
```{r}
#instruction
#gọi tên 3 tiêu chí này lần lượt là:
1) Sinh (vi khuẩn, ...)
2) Lý (màu sắc)
3) Hóa (nước, lipid)


```









```{r}

# check inviduals
fviz_pca_ind(res.PCA, 
             col.ind = salmon.data$origin,
             repel = TRUE # Avoid text overlapping (slow if many points)
             )

#check if Region is relevant to the distribtion of data
fviz_pca_ind(res.PCA, habillage = 18,
             addEllipses =TRUE, ellipse.type = "confidence",
             palette = "jco", repel = TRUE) 

```



```{r}
salmon.data.copy <- salmon.data[2:18]

res.pca <-  PCA(salmon.data.copy, scale.unit = TRUE,quali.sup=17,graph = F)


dimdesc(res.pca)
```
So, considering the dimdesc we can conclude that.

We can classify the salmon best (Dim1) by using (latic.flora):
                   correlation      p.value
lactic.flora         0.9027708 9.041485e-12

With this measurement, we can classify the following Origin
                 Estimate    p.value
origin=Belgium   2.871677 0.02182312
origin=UK        2.208683 0.03851838
origin=Ireland  -2.788912 0.03325308
origin=Scotland -3.662799 0.02354381


We can classify the salmon best (Dim2) by using (a):
                   correlation      p.value
a   0.8778081 1.890503e-10

With this measurement, we can classify the following Origin
                 Estimate    p.value
origin=DK -2.154718 0.02308554


```{r}

# Create the plot
ggplot(temperature, aes(x = latic.flora, y = a, color = Region)) +
  geom_point(size = 5 +
  
  labs(title = "Circle Diagram of Temperature",
       y = "Latitude")


#Create Lat-Long Mean temperature color coded by Region
# Calculate the radius for each circle based on the temperature
temperature$rd_var <- sqrt(temperature$Var / pi)

# Create the plot
ggplot(temperature, aes(x = Long, y = Lati, color = Region)) +
  geom_point(size = temperature$rd_var * 5) +
  
  labs(title = "Circle Diagram of Variance of Temperature",
       y = "Latitude")


```


