---
title: "temperatura"
output: html_document
date: "2024-03-19"
---

```{r}
library(readr)
library(ggplot2)
library(janitor)
library(tidyverse)

csv_url <- "https://raw.githubusercontent.com/tradanghi1999/RStudy/main/pca/temperat.csv"
temperature <- read_delim(csv_url, delim = ";", col_names = TRUE,locale = locale(encoding = "latin1"))


city_dict <- data.frame(French = c("Amsterdam", "Athènes", "Berlin", "Bruxelles", "Budapest", "Copenhague", "Dublin", "Helsinki", "Kiev", "Cracovie", "Lisbonne", "Londres", "Madrid", "Minsk", "Moscou", "Oslo", "Paris", "Prague", "Reykjavik", "Rome", "Sarajevo", "Sofia", "Stockholm", "Anvers", "Barcelone", "Bordeaux", "Edimbourg", "Francfort", "Genève", "Gènes", "Milan", "Palerme", "Séville", "St. Pétersbourg", "Zurich"),
                       English = c("Amsterdam", "Athens", "Berlin", "Brussels", "Budapest", "Copenhagen", "Dublin", "Helsinki", "Kiev", "Krakow", "Lisbon", "London", "Madrid", "Minsk", "Moscow", "Oslo", "Paris", "Prague", "Reykjavik", "Rome", "Sarajevo", "Sofia", "Stockholm", "Antwerp", "Barcelona", "Bordeaux", "Edinburgh", "Frankfurt", "Geneva", "Genoa", "Milan", "Palermo", "Seville", "St. Petersburg", "Zurich"))

#change column name
colnames(temperature)<-c("City","Jan","Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec", "Mean", "Ampl", "Lati", "Long", "Region")


temperature$Var <- apply(temperature[, c("Jan","Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec")], 1, var)

temperature$City <- str_replace_all(temperature$City, city_dict$French, city_dict$English)





#temperature_filtered <- temperature[temperature$Region == "Quest", ]

temperature_long <- tidyr::gather(temperature, key = "Month", value = "Temperature", Jan:Dec)


#color-coded by region
ggplot(temperature_long, aes(x = Month, y = Temperature, group = City, color = Region)) +
  geom_line() +
  theme_minimal() +
  labs(title = "Monthly Temperature by City",
       x = "Month",
       y = "Temperature (°C)")



#Create Lat-Long Mean temperature color coded by Region
# Calculate the radius for each circle based on the temperature
temperature$rd_mean <- sqrt(temperature$Mean / pi)

# Create the plot
ggplot(temperature, aes(x = Long, y = Lati, color = Region)) +
  geom_point(size = temperature$rd_mean * 5) +
  
  labs(title = "Circle Diagram of Temperature",
       y = "Latitude")


#Create Lat-Long Mean temperature color coded by Region
# Calculate the radius for each circle based on the temperature
temperature$rd_var <- sqrt(temperature$Var / pi)

# Create the plot
ggplot(temperature, aes(x = Long, y = Lati, color = Region)) +
  geom_point(size = temperature$rd_var * 5) +
  
  labs(title = "Circle Diagram of Variance of Temperature",
       y = "Latitude")





#scale_x_continuous(limits = c(-123, -117)) +
#scale_y_continuous(limits = c(33, 38)) +


#library(rworldmap)


#sPDF <- joinCountryData2Map(temperature,
                         #   joinCode = "NAME",
                          #  nameJoinColumn = "City")

#dF <- sPDF@data



#temperature$ID <- seq_along(temperature[, 1])

```

As the diagram (1) points out, the researcher thought that would be some dependence between the temperature and the region of these regions

The digram (2) also show that, there is maybe some tendency that city near the south-western corner is a little bit hotter


We then can use the PCA for deeper analysis
```{r}

library(FactoMineR)
library(factoextra)
library(ggplot2)
library(corrplot)

# pca model
res.PCA <-  PCA(temperature, scale.unit = TRUE, quanti.sup=c(14,15,16,17,19,20,21),quali.sup=c(1,18),graph = F)


#print the eigenvalue
print(get_eigenvalue(res.PCA))

#check The quality of representation
var <- get_pca_var(res.PCA)
print(corrplot(var$cos2, is.corr=FALSE))

# Color by cos2 values: quality on the factor map
fviz_pca_var(res.PCA, col.var = "cos2",
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"), 
             repel = TRUE # Avoid text overlapping
             )


#check contribution of variance to PC
# Contributions of variables to PC1
fviz_contrib(res.PCA, choice = "var", axes = 1, top = 12)
# Contributions of variables to PC2
fviz_contrib(res.PCA, choice = "var", axes = 2, top = 12)





# check inviduals
fviz_pca_ind(res.PCA, col.ind = "cos2", 
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
             repel = TRUE # Avoid text overlapping (slow if many points)
             )
#check if Region is relevant to the distribtion of data
fviz_pca_ind(res.PCA, habillage = 18,
             addEllipses =TRUE, ellipse.type = "confidence",
             palette = "jco", repel = TRUE) 




```

```{r}
#Dimension descriptionddim
#temperature$City <- sample(100, size = nrow(temperature), replace = TRUE)



#temperature$Region <- unclass(temperature$Region)

# pca model
temperature.copy <- temperature

indicator_mapping <- c("Ouest" = 1, "Sud" = 2, "Est" = 3, "Nord" = 4)
temperature.copy$Region <-  indicator_mapping[temperature.copy$Region]
temperature.copy <- temperature.copy[2:21]

res.pca <-  PCA(temperature.copy, scale.unit = TRUE, quanti.sup=c(13,14,15,16), quali.sup = 17,graph = F)


dimdesc(res.pca)

```


As we can see from the eigenvalue table, that only Dim1 and Dim2 have eigenvalue > 1, which mean we could keep these PC. Total cumulative.variance.percent > 95%, which mean this model is good enough.

Variables that are away from the origin (JAN - DEC) so they are well represented on the factor map (Dim1 & Dim2).

As can be seen from the graph that Region variable is considered not relevant to the distribution of the data point out on PCA

In conclusion with the dimdesc we can conclude that the Mean is really correlated to Dim1 > 99%, and we could consider that Dim1 is Mean. About Dim2 it is really correlated to Ampl (|max - min|) but cannot consider it as Ampl. We consider Dim2 to be unnamed. 

